Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2016-02-13 manuscript/text_reuse.tex
title
updated ncsl results
ncsl analysis w/o same state dyads
updated policy description

\title{Text as Policy: Identifying Equivalent State Bills through Text Reuse}
\date{\today}
\author{Bruce Desmarais, Matt Burgess, Fridolin Linder, Eugenia Giraudi}

@@

Before

@@

We use three strategies in order to assess the validity of text reuse as a measure of policy equivalence. First, we apply topic models to the sequences that are identified by the SW algorithm as matching sequences. This provides a rough idea of how many of the alignments are substantial and how much procedural language and not substantively significant language gets picked up by the algorithm. Second, we analyze how well the bill similarity aggregated to the state level corresponds with policy diffusion networks identified in previous research \citep{desmarais2015}. And third, we assess the correlation of the distance of the sponsors of a bill dyad and the dyads alignment scores. If substantive policy content, and importantly, the same ideological direction of the provisions is detected by the alignment algorithm, we will expect a high negative correlation between these two measures.

>>>>

\title{Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse}
\date{\today}
\author{Bruce Desmarais, Matt Burgess, Fridolin Linder, Eugenia Giraudi}

@@

Before we describe the algorithm we use for detecting text re-use, and validate that algorithm, we should clearly define the latent variable we seek to measure through the assessment of text overlap. The latent variable that we argue below is measured effectively through text re-use is {\em policy similarity}. The text in legislation is an aggregate representation of the dimensions underlying the policies proposed therein. These dimensions include the domain of the policy, the ideological position enacted by the policy, the level of specificity in the policy enactment, and several other salient features of policy that are communicated through the text in legislation. We do not claim that the re-use of text can be used to measure these dimensions in a specific, disaggregated way. Rather, text re-use serves as a summary measure of similarity across all relevant policy dimensions represented in legislative text.

@@

We use three strategies in order to assess the validity of text reuse as a measure of policy equivalence. First, we apply topic models to the sequences that are identified by the SW algorithm as matching sequences. This provides a rough idea of how many of the alignments are substantial and how much procedural language and not substantively significant language gets picked up by the algorithm. Second, we analyze how well the bill similarity aggregated to the state level corresponds with policy diffusion networks identified in previous research \citep{desmarais2015}. And third, we assess the correlation of the distance of the sponsors of a bill dyad and the dyads alignment scores. If substantive policy content, and importantly, the same ideological direction of the provisions is detected by the alignment algorithm, we will expect a high negative correlation between these two measures.
\subsection{NCSL Tables}

\begin{table}[ht!]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{lll}
               & alignment & no alignment \\
not same table & 11        & 232287       \\
same table     & 3083      & 20639       
\end{tabular}
\end{table}
